\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}

%\acmPrice{15.00}


\begin{document}
\title{Disjunctive Interconnection Graph Integration \\for Disease Gene Prioritization}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Dinh Tran Van}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Padova}
  \streetaddress{Via Trieste, 63}
  \city{Padova} 
  \state{Italy} 
  \postcode{35121}
}
\email{dinh@math.unipd.it}

\author{Alessandro Sperduti}
%\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{University of Padova}
  \streetaddress{Via Trieste, 63}
  \city{Padova} 
  \state{Italy} 
  \postcode{35121}
}
\email{sperduti@math.unipd.it}

\author{Fabrizio Costa}
%\authornote{This author is the
%  one who did all the really hard work.}
\affiliation{%
  \institution{University of Exeter}
  \streetaddress{Exeter EX4}
  \city{Exeter} 
  \country{United Kingdom}}
\email{f.costa@exeter.ac.uk}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
Disease-Gene associations are normally inferred through gene relations which are best represented in form of graphs. Many research are conducted to find out gene relation network by focusing on different aspect of gene expressions. As a consequence, there exist different gene networks. This brings scientists a great opportunity  to have more unified views of genes. Graph integration, therefore, is a logical problem which needs to be effectively solved if we desire to build high performance of disease-gene association inferred systems. In this paper, we propose a novel method for disease gene prioritization. The method owns its strength from an efficient graph integration paradigm which allows to simultaneously capture topological features from all graphs to define gene similarities. Results from two experiments conducted on real datasets prove that our method is the state of the art for disease gene prioritization.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}


\keywords{Graph integration, disease gene prioritization, graph node kernels, graph decomposition}


\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography} 

\end{document}
